Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-18 report/report.tex
Flesh out collision study implementation

\subsection{Feature overlap algorithm}

Outline of the feature overlap algorithm (Go over all features)
Since only road collisions are of interests, all roads were added to a queue and gone over one by one.

The boundary polygon of the buildings are extracted, as well as the polylines of the roads.

To speed up the collision checking process, a geometric hashing solution was developed.
This way feature collision lookup could be made without comparing a feature to all other available features, but instead from a selection of the closest candidates.
The hash bucket size was 230 meters and a feature could be in multiple hash buckets.

Special cases: Where two roads intersect though they share a node.
Then this is a natural connection in the road network and should not be counted as a problematic case of feature overlap.
Also ignored collisions between tunnels and bridges and other roads since these are of different heights.
These were identified by looking at feature attributes in OSM.
Any roads that were represented as polygons or multipolygons instead of plylines were also excluded from the study.

\subsection{Projected edge distance}

Outline of the minimum edge distance algorithm.

@@

% Monday
% TODO: Write Collision study implementation section
% TODO: Edge distance algorithm, algorithm
% Collision study implementation
    % TODO: Figure detailing the steps in the point-matching algorithm

>>>>

\subsection{Feature Overlap algorithm}

The algorithm for determining feature overlap will calculate how many features and how many of their edges are intersecting with some other feature or edge.
It will also calculate the total length of all edge which are overlapping with some other edge.

The algorithm begins by iterating over all road features.
Let $A$ be the current road feature.
Since only road collisions are of interests, all roads were added to a queue and gone over one by one.
The polyline of the current road feature is extracted.
Then, all other candidate features for collision are iterated over, and their boundary polygons (for buildings) or polylines (for roads) are extracted.
Let $B$ be the current feature, road or building, that is being compared to $A$.
The algorithm then iterates over each edge $e_a$ in the polyline of $A$, and each edge $e_b$ in the polyline or polygon of $B$.
The Projected Line Segment Distance algorithm (See section 4.2.3) is used to determine the shortest distance between $e_a$ and $e_b$, and the smallest distance between any combination of edges $e_a$ and $e_b$ is taken to be the shortest distance between features $A$ and $B$.
If this distance is smaller than the minimum width of $A$, then $A$ and $B$ are colliding.

To speed up the collision checking process, a geometric hashing solution was developed.
In this way, feature collision lookup could be made without comparing a feature to all other available features, but instead from a selection of the closest candidates.
The hash bucket size was 230 by 230 meters and a feature could be in multiple hash buckets.

Here a few special cases are noted:
\begin{enumerate}
    \item If two roads intersect even though they share a node, it is a natural connection in the road network and should not be counted as a problematic case of feature overlap.
    \item Collisions between tunnels or bridges and other roads were ignored since these are of different heights. Brdiges and tunnels were identified by looking at feature attributes in OSM.
    \item Any roads that were represented as polygons or multipolygons instead of ploylines were also excluded from the study. These are typically town squares or areas designated for walking.
\end{enumerate}

\subsection{Projected Line Segment Distance}

The Projected Line Segment Distance (PLSD) algorithm is an extented version of the Line Segment Distance (LSD) algorithm.
Whereas LSD simply measures the distance between the two absolute closest points on two line segments, PLSD will yield the distance of the shortest vector $v$ between line segments $e_a$ and $e_b$, with the condition that $v$ is perpendicular to the tangent of $e_a$.
In the Feature Overlap algorithm, using the same notation as in section 4.2.2, PLSD takes $e_a$ to be the current edge of road feature $A$, and $e_b$ to be the current edge of feature $B$ (road or building).
See Algorithm 2 for a detailed view of the PLSD algorithm.

@@

% Monday
% TODO: Edge distance algorithm, algorithm
% Collision study implementation
    % TODO: Figure detailing the steps in the point-matching algorithm
